Chromosomal duplication can be an evolutionary detour on the path to adaptation

### 2022-09-13 ms/ms.tex
small revision based on IK comment

\paragraph{Sensitivity analysis.} 
Changing a single parameter while keeping the rest fixed at the MAP estimate produces a worse fit to the data~(\Cref{fig:sensitivity}).
Furthermore, we fitted models with a mutation rate fixed at $\mu=10^{-5}$, $10^{-6}$ and $10^{-7}$.
We inferred similar parameters estimates for the model with $\mu=10^{-6}$ compared to the model with a free $\mu$ parameter, in which the inferred mutation rate is $\mu \approx 3\cdot10^{-6}$.
Inference assuming $\mu=10^{-5}$ or $\mu=10^{-7}$ produced a higher estimate of the aneuploidy rate, $\delta$; assuming $\mu=10^{-7}$, the estimated fitness of \anwt\ was lower; otherwise, estimates were similar to our main model (\Cref{fig:mu}).

>>>>

\paragraph{Sensitivity analysis.} 
Changing a single parameter while keeping the rest fixed at the MAP estimate produces a worse fit to the data~(\Cref{fig:sensitivity}).
Furthermore, we fitted models with a mutation rate fixed at $\mu=10^{-5}$, $10^{-6}$ and $10^{-7}$.
We inferred similar parameters estimates for the model with $\mu=10^{-6}$ compared to the model with a free $\mu$ parameter, in which the inferred mutation rate is $\mu \approx 3\cdot10^{-6}$.
Inference assuming $\mu=10^{-5}$ or $\mu=10^{-7}$ produced similar estimates except that the estimated aneuploidy rate, $\delta$, was higher, and assuming $\mu=10^{-7}$, the estimated fitness of \anwt\ was lower (\Cref{fig:mu}).
